\documentclass[fontsize=10]{scrartcl}
\reversemarginpar

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}}

\usepackage{multicol}

\usepackage{hyperref}
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon}

\usepackage{enumitem}
\setlist{leftmargin=2.5mm}

\usepackage[nochapters]{classicthesis}
\usepackage[]{kpfonts}

\usepackage{xcolor}
\definecolor{Maroon}{RGB}{128,0,0}

\newlength{\datebox}\settowidth{\datebox}{00000000000000}
\newlength{\longdatebox}\settowidth{\longdatebox}{0000000000000000}

\newcommand{\NewEntry}[2]{\noindent\hangindent=1em\hangafter=0 \parbox{\longdatebox}{\small \textit{#1}}\hspace{1.5em} #2
	\vspace{0.25em}}

\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\small{#1}\par\normalsize\vspace{0.75em}}

\renewcommand\labelitemi{--}

\newcommand{\cventry}[4]
{
	\noindent \large \textscsl{#2} \MarginText{#3} 
	\hfill \parbox{\datebox}{\textit{\small #1}}
	\small 
	\begin{itemize}
		\item #4
	\end{itemize}
	\normalsize \vspace{0.75em}
}

\newcommand{\cvsection}[1]{\vspace{1em} {\color{Maroon}\hspace{-2.5em} \Large\spacedlowsmallcaps{#1}\vspace{.75em}}}

\usepackage[letterpaper, top=1in,right=1in,bottom=1.5in,left=2in]{geometry}

\begin{document}
	
	\vspace*{-2em} 
	{\hspace{-10em} \LARGE \color{Maroon} \textsc{Grant Baldwin}} \\
	
	\NewEntry{e-mail}{\href{mailto:gkbaldwin2002@gmail.com}{gkbaldwin2002@gmail.com}}
	
	\NewEntry{phone}{404-414-2842}
	
	\NewEntry{github}{\href{https://www.github.com/eyz11327}{github.com/eyz11327}}
	
	\NewEntry{citizenship}{United States of America citizen}
	
	\vspace{1em}
	
	\cvsection{Professional Experience}
	
	\cventry
	{Apr '25 -- Present}
	{Systems Engineer II}
	{Charter Communications}
	{
		Identified, developed, and deployed an automation reducing small cell install time by 30+ minutes, projected to save the company \$100k by the end of the year.
		\item Performed a complete re-architecture and refactor on an existing 5G automation to fix consistent reliability, timeliness, and accuracy issues on 3000+ performance indicators for millions of GNBs.
		\item Developed an Ansible playbook to deploy a database server with Postgres + Timescale and integrated LDAP user logins to significantly reduce database user management over time.
		\item Ensured 99\% uptime, monitoring, alerting, consistency, accuracy, and up-to-date documentation on 30+ ETLs all developed and owned by me.
		\item Sole product owner and developer on all 5G automation workflows, supporting multiple full-time data scientists across various teams in the organization. 
		\item Introduced and administered code reviews into the team's weekly workflow to ensure code quality, idea sharing, and continued learning for all technical team members.
	}
	
	\cventry
	{Mar '24 -- Apr '25}
	{Systems Engineer I}
	{Charter Communications}
	{
		Won both the Q3 Quarterly Excellence Award (Aug '24) and the Above and Beyond Award (Oct '24).
		\item Worked with non-technical users across several teams to develop a chat bot used hundreds of times per day providing concise, real-time information on access point information.
		\item Rapidly developed and deployed a breakfix automation to stifle a botnet resulting in quick, easy identification of infected access points, alongside incorporating extensive graphing and alerting on the project using Prometheus and Grafana.
		\item Created a cookiecutter project structure to ensure consistency across the team's developments.
		\item Introduced modern Python practices (e.g., linting, type hinting, virtual environments) improving code clarity, security, and team efficiency.
		\item Developed and deployed several large, containerized ETL automations in Python. One of these ETLs reduced critical missing data from 6\% to 0.6\% for the team's data scientist.
	}

	\cventry
	{June '23 -- Aug '23}
	{Network Automation Intern}
	{Charter Communications}
	{
		Significantly refactored and deployed an automation directly impacting tens of thousands of customers to be more readable, maintainable, and to work as expected.
		\item Helped develop a robust common package for the team to utilize moving forward.
	}

	\cventry
	{May '22 -- Aug '22}
	{Software Engineering Intern}
	{Pie Insurance}
	{
		Worked directly with the quoting team to create and update critical software used to generate insurance quotes, reducing average quote generation time by over 80\%.
	}
	
	\cvsection{Education}
	
	\cventry
	{Aug '20 -- Dec '23}
	{Undergraduate Computer Science + Business Minor}
	{Colorado School of Mines}
	{
		Won class-wide freshmen design competition using a Raspberry Pi running a custom AI.
		\item Dean's list in 2020 and 2021.
		\item Completed upper-level coursework in Computer Graphics, Operating Systems, Algorithms, Data Science, and Information Security \& Privacy.
		\item Took a variety of high level non-coding classes including Risk Communication, Corporate Finance, and Business Strategy.
	}

	\cvsection{Language Proficiency}
	\cventry
	{}{}{}
	{	
		Very proficient in Python and HTML + CSS
		\item Proficient in C, C++, and SQL
		\item Experience with Rust, TypeScript, Java, Kotlin, OCaml and RISC-V
	}

	\cvsection{Familiar Technologies}
	\cventry
	{}{}{}
	{	
		Ansible, Docker, Podman, Linux, Kubernetes, Redis, Grafana, Prometheus, Postgres, CI/CD, Git, SQLAlchemy, Google Apps Script, Wordpress
	}
	
	\cvsection{Interests and Mostly Useless Skills}
	\cventry
	{}{}{}
	{	
		Rock climbing, skiing, hiking national parks, online typing contests, and chess
	}
	
\end{document}
